\LARGE \bf Multi-Armed Bandit Models for 2D Grasp Planning with Uncertainty

### 2015-06-15 paper.tex
New grasp image.

\subsubsection{Thompson Sampling}
The computational cost of determining the Gittins indices can increase rapidly as the discount factor approaches $1$.
However, in the case of finding the best arm, we want to plan for long-term reward and thus want $\gamma$ as close to $1$ as possible.
Due to computational constraints we must use a smaller $\gamma$, but this can lead to the algorithm pulling only the most promising arm for many iterations~\cite{kelly1981multi}.

@@

\section{Grasp Planning Problem Definition}
We consider grasping a rigid planar object from above using parallel-jaw grippers.
We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
We consider uncertainty in shape, pose, gripper approach, and friction coefficient. We assume that the distributions on these quantities are given and can be sampled from.  While we only consider grasping planar objects, our method can work on planar slices of a 3D object. 
\begin{figure}[t!]
\centering
\includegraphics[width = 8.5cm, height = 5.25cm]{figures/bandit_grasp_model.jpg}
\caption{Illustration of our grasping model for parallel jaw grippers on a mechanical switch. Jaw placements are illustrated by a red direction arrow and line. A grasp plan centered at $\by$ (plus symbol) at angle $\psi$ consists of 2D locations for each of the parallel jaws $\bj_1$ and $\bj_2$. When following the grasp plan, the jaws contact the object at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations. Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.}
\vspace*{-2ex}
\label{fig:grasp_model}
\end{figure}

@@

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
The measurement noise were assigned uniformly at random to the SDF.
We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
We  performed experiments for the case of two hard contacts in 2-D.
We drew random grasps $\Gamma$ by uniformly sampling the angle of the grasp axis around a circle with radius $\sqrt{2}
M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
1600 MHz memory in Matlab 2013b. For illustration purposes, Figure \ref{fig:shape_samples} also displays
GPIS models of 2 real-world objects are visualized using the GPIS-Blur method~\cite{mahler2015gp}.

\subsection{Multi-Armed Bandit Experiments}
For our experiments we look at selecting an optimal grasp among $|G| = 1000$ candidates. We draw samples from our
graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. We calculated the expected performance
over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling,
Gittins indices, iterative pruning~\cite{kehoe2012toward} and uniform allocation. Uniform allocation selects a grasp at
random from the set to sample the next candidate and thus does not use any prior information. Iterative pruning prunes
grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the
discount factor $\gamma =0.98$ for the Gittins method, which was the highest we could compute in a reasonable amount of
time due to the exponential growth in computation time with respect to $\gamma$~\cite{gittins2011multi}.

@@

\section{Acknowledgments} 
This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, and by grants from Google. 
We thank the AMPLab, UCBerkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.

>>>>

\subsubsection{Thompson Sampling}
The computational cost of determining the Gittins indices can increase exponentially as the discount factor approaches $1$.
However, in the case of finding the best arm, we want to plan for long-term reward and thus want $\gamma$ as close to $1$ as possible.
Due to computational constraints we must use a smaller $\gamma$, but this can lead to the algorithm pulling only the most promising arm for many iterations~\cite{kelly1981multi}.

@@

\section{Grasp Planning Problem Definition}
We consider grasping a rigid planar object from above using parallel-jaw grippers.
We assume that the interaction between the gripper and object is quasi-static~\cite{kehoe2012estimating, kehoe2012toward}.
We consider uncertainty in shape, pose, gripper approach, and friction coefficient. We assume that the distributions on these quantities are given and can be sampled from.  While we only consider grasping planar objects, our method can work on planar slices of a 3D object. 
\begin{figure}[t!]
\centering
\includegraphics[width = 8.5cm, height = 5.25cm]{figures/bandit_grasp_model.jpg}
\caption{Illustration of our grasping model for parallel jaw grippers on a mechanical switch. Jaw placements are
illustrated by rectangles closing along the dashed line. A grasp plan centered at $\by$ (plus symbol) at angle $\psi$ consists of 2D locations for each of the parallel jaws $\bj_1$ and $\bj_2$. When following the grasp plan, the jaws contact the object at locations $\bc_1$ and $\bc_2$, and the object has outward pointing unit surface normals $\bn_1$ and $\bn_2$ at these locations. Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object.}
\vspace*{-2ex}
\label{fig:grasp_model}
\end{figure}

@@

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown} of 2D objects as in \cite{christopoulos2007handling}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
The measurement noise was assigned uniformly at random to the SDF.
We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
The noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
We  performed experiments for the case of two hard contacts in 2-D.
We drew random grasps $\Gamma$ by uniformly sampling the angle of the grasp axis around a circle with radius $\sqrt{2}
M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
1600 MHz memory in Matlab 2013b. 
Figure \ref{fig:shape_samples} displays examples of GPIS models using the GPIS-Blur method~\cite{mahler2015gp}
as well as resulting grasp samples.

\subsection{Multi-Armed Bandit Experiments}
For our experiments we consider selecting an optimal grasp among $|G| = 1000$ candidates per object. We draw samples from our
graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. We calculated the expected performance
over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling,
Gittins indices, iterative pruning~\cite{kehoe2012toward} and uniform allocation. Uniform allocation selects a grasp at
random from the set to sample the next candidate and thus does not use any prior information. Iterative pruning prunes
grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the
discount factor $\gamma =0.98$ for the Gittins method, which was the highest we could compute in a reasonable amount of
time due to the exponential growth in computation time with respect to $\gamma$~\cite{gittins2011multi}.

@@

\section{Acknowledgments} 
This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, and by grants from Google. 
We thank the AMPLab, UC Berkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Peter Bartlett, Steve McKinley and Dylan Hadfield-Menell.
